Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-12 analysis/paper/paper.Rmd
Add statement about computer and R version used

Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully uppercase to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].

@@

Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] in the R environment [@RCT2020] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
sessionInfo()
```

>>>>

Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardise the capitalisation and alleviate any issues with capitalisation used between evaluators.
A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2021].

@@

The statistical analysis was performed using R version 4.1.0 [@RCT2021] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' [@Burkner2018] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

```{r colophon, cache = FALSE}
# which R packages and versions?
sessioninfo::session_info()
```
